### 2016-12-16 paper58/paper58.Rmd
updated paper58

```{r}
## Generate a map for the PC weights for the different modes of the
## wet-day mean mu annual cycle.
mupcamap <- function(mu,pca,ipca,xlim,ylim,r2) {
  r2 <- as.numeric(r2)
  colpc <- rev(colscal("t2m",n=100))
  cz <- round(100*abs(pca$v[,ipca])/quantile(abs(pca$v[,ipca]),0.95))
  cz[cz > 100] <- 100; cz[cz < 1] <- 1
  col <- colpc[cz]
  pch <- rep(19,length(r2))
  mo <- c(r2) > 0.4
  hi <- c(r2) > 0.6
  pch[!hi] <- 1
  pch[!mo] <- 4
  cex <- 1.5*c(r2) + 0.2

  map(mu, xlim=xlim,ylim=ylim,bg='grey80',new=FALSE)
  points(lon(mu),lat(mu),pch=pch,col=col,cex=cex)
  par(xpd=TRUE)
  text(10,73,paste('Annual cycle in PC',ipca,
      'with variance of',round(100*pca$d[ipca]^2/sum(pca$d^2)),'%'),pos=4)

@@

```{r}
## Show the predictor area:
X <- retrieve('air.mon.mean.nc',lon=c(-100,-30),lat=c(0,40))
map(X,projection='sphere',colbar=list(breaks=seq(8,28,by=0.5)))
figlab('Figure SM3',xpos=0.8,ypos=0.999)
```

>>>>

```{r}
## Generate a map for the PC weights for the different modes of the
## wet-day mean mu annual cycle.
mupcamap <- function(mu,pca,ipca,xlim,ylim,r2) {
  r2 <- as.numeric(r2)
  colpc <- rev(colscal("budrd",n=100))
  print(colpc)
  cz <- round(100*abs(pca$v[,ipca])/quantile(abs(pca$v[,ipca]),0.95))
  cz[cz > 100] <- 100; cz[cz < 1] <- 1
  col <- colpc[cz]
  pch <- rep(19,length(r2))
  mo <- c(r2) > 0.4
  hi <- c(r2) > 0.6
  pch[!hi] <- 1
  pch[!mo] <- 4
  cex <- 1.2*c(r2) + 0.5
  map(mu, xlim=xlim,ylim=ylim,bg='grey90',col='grey90',cex=0.5,new=FALSE)
  points(lon(mu),lat(mu),pch=pch,col=col,cex=cex)
  par(xpd=TRUE)
  text(10,73,paste('Annual cycle in PC',ipca,
      'with variance of',round(100*pca$d[ipca]^2/sum(pca$d^2)),'%'),pos=4)

@@

```{r}
## Show the predictor area:
X <- retrieve('air.mon.mean.nc',lon=c(-100,-30),lat=c(0,40))
map(X,projection='sphere',colbar=list(pal="budrd",breaks=seq(8,28,by=0.5)))
figlab('Figure SM3',xpos=0.8,ypos=0.999)
```
